% vim:foldmethod=marker:fmr=<<<,>>> spell nowrap
\documentclass{article}

\include{preamble.tex}

\setcounter{secnumdepth}{4}
% \RedeclareSectionCommand[runin=false,afterskip=0pt,afterindent=false]{paragraph}

\title{Brothers on the bridge problem}
\author{Sergei Mironov}

\begin{document}

\maketitle
\tableofcontents
\section{Setup}

\begin{python}
import ortools
from ortools.linear_solver import pywraplp
print(ortools.__version__)
\end{python}

\begin{result}
9.4.9999
\end{result}

\begin{codeai}
/reset

You are a helphful assistant. You generate responses using Latex formatting by
default. Thus, whenever you want to create a Python code, you wrap it into a
"python" Latex environment (i.e \verb|begin{<LANG>}| end \verb|{\<LANG\>}| tags
where LANG is "python"). Rather than the default Markdown formatting.  And don't
wrap it into equation \verb|\[| or \verb|\]| tags! When you generate a plain
text, escape any undersores character with a backslash, like this: \verb|\_|.
For verbatim text, Instead of `text` use \\verb|text|.  For bold text, instead
of \verb|**text**| use \textbf{text}. For italic text, instead of \verb|*text*|
use \\textit{text}. For better paragraph separation you can use \verb|\vsp| tag
(vertical space). For numbered lists, use \verb|\begin{enumerate}| ...
\verb|\item| ..  \verb|\item| ...  \verb|\end{enumerate}|. For lists, use
\verb|\begin{itemize}| ... \verb|\item| .. \verb|\item| ...
\verb|\end{itemize}|. \verb|\problem| and \verb|\ans| just print these words in
bold. Always consider that one should always be able to paste the text you
generate between \verb|\begin{document}| and \verb|\end{document}|. For tikz
pictures, use just \verb|\begin{...}| .. \verb|\end{...}| without additional
verbatim markup. Never use \verb|```| as in Markdown! For Python code, use
2-space indentation.

/read model prompt

Hi Model. Please generate me a \textbf{Hello-World} Python
program. Please write a short description demonstrating the usage of
underscores.
\end{codeai}

\begin{result}
Here's a simple Python program that prints \textbf{Hello, World} to the console:

\begin{python}
# This is a simple Python program that prints "Hello, World" to the console.

def print_hello_world():
  print("Hello, World!")

print_hello_world()
\end{python}

\vsp

### Description

In this program:

- We define a function named \verb|print_hello_world|. Note that in Python,
underscores are commonly used to separate words in function and variable names.
This is called \textit{snake\_case} naming convention.
- Inside the function, we use the \verb|print| function to output the string
\textbf{Hello, World}.
- Finally, we call the function to execute the code and display the message.

You can run this script in any Python environment to see the output.
\end{result}

\section{Conversation}

\subsection{The problem}

\begin{ai}
Ok. Now lets write a linear solver using Google ortools Python package. I will
need to solve the following task.

\vsp
Four brothers want to cross a suspension bridge at night. The bridge can hold a
maximum of 2 people together with a flashlight. They only have one flashlight
between them, which means someone will need to bring it back across the bridge
each time. Each brother crosses at a different speed: the oldest brother can
cross the bridge in 1 minute, the second can cross in 2 minutes, the third in 5
minutes, and the youngest in 10 minutes.

The task is to determine the minimum time required for all the brothers to cross
the bridge.

\vsp
Please import the solver and add the boolean variables \verb|x_t_b| where
\verb|t| is the moment of time and `b` is the brother index.
\end{ai}
% Format your response as a fragment of a LaTeX document which could be pasted
% between begin and end document tags. No LaTeX preamble is needed.  That is,
% never use ``` or any other Markdown-style backtick markup. Use the
% \verb|\begin{XXX}| and \verb|\end{XXX}| tags for code sections instead where
% XXX is python for the python language.
% Please don't print ```latex or similar backticks!

\begin{airesult}
To solve this problem using the Google OR-Tools Python package, we can use a
linear solver with boolean variables that represent whether a brother is
crossing or not at a particular time. The goal is to minimize the overall
crossing time.

Below is the setup of the problem in Python using Google OR-Tools.

\vsp

\begin{python}
from ortools.linear_solver import pywraplp

# Create the solver
solver = pywraplp.Solver.CreateSolver('SCIP')

# Define the crossing times for each brother
crossing_times = [1, 2, 5, 10]

# Maximum possible time based on reasoning is the sum of all crossing times
max_time = sum(crossing_times)

# Define boolean variables x_t_b
# x_t_b indicates if brother b (0 <= b < 4) is crossing at time t (0 <= t <
# max_time)
x = {}
for t in range(max_time):
    for b in range(4):  # 4 brothers
        x[t, b] = solver.BoolVar(f'x_{t}_{b}')

# Additional constraints and objective function will be added here to minimize
# the total crossing time

# Here, you would define the constraints ensuring only two brothers cross at
# once with the flashlight
# and one returns it, while aiming to minimize the total crossing time.

# Solve the problem
status = solver.Solve()

# Check the status and print the result if optimal
if status == pywraplp.Solver.OPTIMAL:
    print('Solution found!')
    # Retrieve and print the solution here
else:
    print('The problem does not have an optimal solution.')
\end{python}

\vsp

This code sets up the infrastructure necessary for modeling the problem. You
need to add additional constraints to ensure that the brothers cross the bridge
in pairs and one returns the flashlight, as well as specifying the objective
function to minimize the total crossing time.
\end{airesult}


\subsection{Solvers}

\begin{ai}
What is the difference between the SCIP and the CpModel solvers of or-tools?

Format your response as a fragment of a LaTeX document which could be pasted
between begin and end document tags. No LaTeX preamble is needed.  That is,
never use ``` or any other Markdown-style backtick markup. Use the
\verb|\begin{XXX}| and \verb|\end{XXX}| tags for code sections instead. For
python, set XXX to python.
\end{ai}

\begin{airesult}
\vsp

The SCIP and CpModel solvers in OR-Tools are designed for different types of
optimization problems, reflecting their distinct methodologies and use cases:

\begin{itemize}
    \item \textbf{SCIP Solver}:
    \begin{itemize}
        \item SCIP (Solving Constraint Integer Programs) is a framework for
              solving mixed integer programming (MIP) problems, particularly
              focusing on linear and integer constraints.
        \item It is widely used for linear optimization tasks where the decision
              variables are either continuous or integer.
        \item SCIP is capable of handling large-scale problems and can utilize
              integer and linear constraints to find optimal solutions
              efficiently.
    \end{itemize}

    \item \textbf{CpModel Solver}:
    \begin{itemize}
        \item CpModel (Constraint Programming Model) is tailored for constraint
              programming problems, where variables can take on discrete values
              within specific domains.
        \item It excels at problems involving complex constraints, such as
              scheduling and combinatorial problems, where the relationships
              between variables are not necessarily linear.
        \item CpModel is designed to handle logical, arithmetic, and custom
              constraints to explore feasible solutions across a diverse problem
              space swiftly.
        \item The solver uses sophisticated search techniques and heuristics to
              tackle these highly combinatorial problems.
    \end{itemize}
\end{itemize}

\vsp

In summary, if you're working with linear equations and mixed integer
programming, you would typically use SCIP. On the other hand, if your problem
involves complex combinatorial constraints and logical conditions, CpModel is a
more suitable choice.
\end{airesult}


\subsection{Variable multiplication}

In constraint programming with OR-Tools' \verb|CpModel|, direct multiplication
of two decision variables is not inherently supported within the expressions you
print or similar contexts. Instead, you need to use auxiliary variables and
additional constraints to simulate such products.

To implement this, you can introduce an auxiliary variable to represent the
product and enforce it using the \verb|AddMultiplicationEquality| method:

\vsp

\begin{python}
# Create an auxiliary variable for the product of x[0,0,0] and x[0,0,1]
product_var = model.NewIntVar(0, 1, 'product_var')

# Add multiplication equality as a constraint
model.AddMultiplicationEquality(product_var, [x[0,0,0], x[0,0,1]])

# After solving the model, print the value of the auxiliary product variable
solver = cp_model.CpSolver()
status = solver.Solve(model)

if status == cp_model.OPTIMAL:
  print('Product of x[0,0,0] and x[0,0,1] =', solver.Value(product_var))
else:
  print('The problem does not have an optimal solution.')
\end{python}

\vsp

In this code:

\begin{itemize}
    \item An auxiliary variable \verb|product_var| represents the product of
\verb|x[0,0,0]| and \verb|x[0,0,1]|.
    \item The \verb|AddMultiplicationEquality| enforces that this variable
equals the product of the given decision variables.
    \item You can then solve the model and query the value of \verb|product_var|
to get the product of the original variables.
\end{itemize}

This approach ensures you can evaluate and make use of "products" of decision
variables within a constraint programming context.

\section{Implementation}

\subsection{The solve function}

\begin{python}
from ortools.sat.python import cp_model

def solve(crossing_times, max_time):
  # Create the CpModel
  model = cp_model.CpModel()

  # Number of brothers
  N = len(crossing_times)

  # Define boolean variables x_t_d_b
  # x_t_d_b indicates if brother b (0 <= b < 4) is crossing at time t (0 <= t <
  # max_time) in direction d (0 or 1)
  x = {}
  for b in range(N):  # N brothers
    for t in range(max_time):  # time moments
      for d in [0, 1]:  # Direction
        x[t, d, b] = model.NewIntVar(0, 1, f'x_{t}_{d}_{b}')

  # Constraint: No more than two brothers can be on the bridge in any direction
  # at any time
  num_brothers_crossing = lambda t,d: sum(x[t, d, b] for b in range(N))
  for t in range(max_time):
    for d in [0, 1]:
      model.Add(num_brothers_crossing(t,d)<=2)

  # Constraint: All brothers should have crossed the bridge in direction 0
  # by the last time moment
  brother_crossed = lambda b: sum([x[t,0,b] - x[t,1,b] for t in range(max_time)])
  for b in range(N):
    model.Add(brother_crossed(b)==1)

  # Constraint: law of brothers preservation. For all time moments, a brother can
  # only cross the bridge in dir 0 if the sum of his past crossings equals to 0.
  brother_position = lambda b,t: sum(x[tpast,0,b] - x[tpast,1,b] for tpast in range(t+1))
  brother_position2 = lambda b,t: sum(x[tpast,0,b] - x[tpast,1,b] for tpast in range(t)) + x[t,0,b]
  for b in range(N):
    for t in range(max_time):
      model.Add(   brother_position(b,t)<=1)
      model.Add(0<=brother_position(b,t))
      model.Add(   brother_position2(b,t)<=1)
      model.Add(0<=brother_position2(b,t))

  # Constraint: the flashlight should be returned if people remain on the left side
  brothers_on_the_right_side = lambda t: sum(x[t,0,b]+sum(x[tp,0,b]-x[tp,1,b] for tp in range(t)) for b in range(N))
  brothers_went_left = lambda t : sum(x[t,1,b] for b in range(N))
  for t in range(max_time):
    model.Add(N*brothers_went_left(t) >= N - brothers_on_the_right_side(t))
    #model.Add(brothers_went_left(t)>0)


  # Calculate the total crossing time considering the minimum speed when two
  # brothers cross together
  xx = {}
  for t in range(max_time):
    for d in [0,1]:
      for b1 in range(N):
        for b2 in range(b1+1, N):
          ba=min(b1,b2)
          bb=max(b1,b2)
          xx[t,d,ba,bb] = model.NewIntVar(0, 1, f'xx_{t}_{d}_{ba}_{bb}')
          model.AddMultiplicationEquality(xx[t,d,ba,bb], [x[t,d,ba], x[t,d,bb]])
  brother_go_alone = lambda t,d,b : x[t,d,b]-sum(xx[t,d,min(b,b2),max(b,b2)] for b2 in range(N) if b!=b2)
  brothers_go_in_pair = lambda t,d,b1,b2 : xx[t, d, b1, b2]
  total_crossing_time = sum(brothers_go_in_pair(t, d, b1, b2)*
                            max(crossing_times[b1], crossing_times[b2])
                            for b1 in range(N)
                            for b2 in range(b1 + 1, N)  # Ensure b1 != b2
                            for d in [0,1]
                            for t in range(max_time)) + \
                        sum(brother_go_alone(t,d,b)*crossing_times[b]
                            for b in range(N)
                            for d in [0,1]
                            for t in range(max_time))


  # Set the objective to minimize the total crossing time
  model.Minimize(total_crossing_time)

  # Create a solver and solve the model
  solver = cp_model.CpSolver()

  # Solve the model
  status = solver.Solve(model)

  # Check the status and print the result if optimal
  if status == cp_model.OPTIMAL:
    print('Solution found!', solver.Value(total_crossing_time))
    # Retrieve and print the solution here
    for t in range(max_time):
      for d in [0, 1]:
        crossing_brothers = []
        for b in range(N):
          # print(x[t, d, b], '---->', solver.Value(x[t, d, b]))
          if solver.Value(x[t, d, b]) == 1:
            crossing_brothers.append(b)
        if crossing_brothers:
          print(f'Time {t}, Direction {d}: Brothers {crossing_brothers} crossing')
      #print('Time', t, 'brothers_on_the_right_side', solver.Value(brothers_on_the_right_side(t)))
      #print('Time', t, 'brothers_went_left        ', solver.Value(brothers_went_left(t)))
      #for b in range(N):
      #  print('Time', t, f'brother {b} positions       ', solver.Value(brother_position2(b,t)), \
      #        ',', solver.Value(brother_position(b,t)))
      #  print('Time', t, f'brother {b} go_alone        ', solver.Value(brother_go_alone(t,0,b)), \
      #                                                 solver.Value(brother_go_alone(t,1,b)))
  else:
    print(f'The problem does not have an optimal solution: {status}.')

\end{python}

\subsection{Experiments}

\begin{python}
# Define the crossing times for each brother
crossing_times = [1, 2, 5, 10]
# Maximum possible time based on reasoning is the sum of all crossing times
max_time = 8
solve(crossing_times, max_time)
\end{python}

\begin{result}
Solution found! 17
Time 0, Direction 0: Brothers [0, 1] crossing
Time 0, Direction 1: Brothers [0] crossing
Time 1, Direction 0: Brothers [2, 3] crossing
Time 1, Direction 1: Brothers [1] crossing
Time 2, Direction 0: Brothers [0, 1] crossing
\end{result}

\begin{python}
# Define the crossing times for each brother
crossing_times = [1, 3, 8, 12]
# Maximum possible time based on reasoning is the sum of all crossing times
max_time = 8
print("Crossing times", crossing_times)
solve(crossing_times, max_time)
\end{python}

\begin{result}
[1, 3, 8, 12]
Solution found! 22
Time 0, Direction 0: Brothers [0, 1] crossing
Time 0, Direction 1: Brothers [0] crossing
Time 1, Direction 0: Brothers [2, 3] crossing
Time 1, Direction 1: Brothers [1] crossing
Time 2, Direction 0: Brothers [0, 1] crossing
\end{result}

\begin{python}
crossing_times = [1,3,9,9,14]
print("Crossing times", crossing_times)
solve(crossing_times, 10)
\end{python}

\begin{result}
Crossing times [1, 3, 9, 9, 14]
Solution found! 34
Time 0, Direction 0: Brothers [0, 1] crossing
Time 0, Direction 1: Brothers [0] crossing
Time 1, Direction 0: Brothers [0, 4] crossing
Time 1, Direction 1: Brothers [0] crossing
Time 2, Direction 0: Brothers [2, 3] crossing
Time 2, Direction 1: Brothers [1] crossing
Time 3, Direction 0: Brothers [0, 1] crossing
\end{result}

\begin{python}
crossing_times = [1,1,2,5,10]
print("Crossing times", crossing_times)
solve(crossing_times, 10)
\end{python}

\begin{result}
Crossing times [1, 1, 2, 5, 10]
Solution found! 17
Time 0, Direction 0: Brothers [0, 1] crossing
Time 0, Direction 1: Brothers [1] crossing
Time 1, Direction 0: Brothers [1, 2] crossing
Time 1, Direction 1: Brothers [1] crossing
Time 2, Direction 0: Brothers [3, 4] crossing
Time 2, Direction 1: Brothers [0] crossing
Time 3, Direction 0: Brothers [0, 1] crossing
\end{result}

\begin{python}
crossing_times = [1,1,2,5,10,15,25,34,23]
print("Crossing times", crossing_times)
solve(crossing_times, 10)
\end{python}

\begin{result}
Crossing times [1, 1, 2, 5, 10, 15, 25, 34, 23]
Solution found! 80
Time 0, Direction 0: Brothers [0, 1] crossing
Time 0, Direction 1: Brothers [0] crossing
Time 1, Direction 0: Brothers [5, 8] crossing
Time 1, Direction 1: Brothers [1] crossing
Time 2, Direction 0: Brothers [1, 2] crossing
Time 2, Direction 1: Brothers [1] crossing
Time 3, Direction 0: Brothers [0, 1] crossing
Time 3, Direction 1: Brothers [0] crossing
Time 4, Direction 0: Brothers [3, 4] crossing
Time 4, Direction 1: Brothers [1] crossing
Time 5, Direction 0: Brothers [0, 1] crossing
Time 5, Direction 1: Brothers [1] crossing
Time 6, Direction 0: Brothers [6, 7] crossing
Time 6, Direction 1: Brothers [0] crossing
Time 7, Direction 0: Brothers [0, 1] crossing
\end{result}

\section{Model checks}

\subsection{Checking the times: 1,3,8,12. (Correct, the solution is 22)}

\begin{ai}
/reset


Consider the following problem:

Four brothers want to cross a suspension bridge at night. The bridge can hold a
maximum of 2 people together with a flashlight. They only have one flashlight
between them, which means someone will need to bring it back across the bridge
each time. Each brother crosses at a different speed: the oldest brother can
cross the bridge in 1 minute, the second can cross in 3 minutes, the third in 8
minutes, and the youngest in 12 minutes.

The task is to determine the minimum time required for all the brothers to cross
the bridge.

Please use Latex markup for lists, enumerations, bold, italic and everything.
\end{ai}

\begin{airesult}
\vsp

\textbf{Solution:}

The brothers need to make strategic decisions for crossing the bridge
efficiently. Let us label the brothers as:

\begin{itemize}
  \item Brother A: Crosses in 1 minute
  \item Brother B: Crosses in 3 minutes
  \item Brother C: Crosses in 8 minutes
  \item Brother D: Crosses in 12 minutes
\end{itemize}

The strategy to minimize the total time involves using the faster brothers to
bring the flashlight back. Here's a step-by-step breakdown:

\vsp

\textbf{Steps}

\begin{enumerate}
  \item Brother A and Brother B cross the bridge together.
    \begin{itemize}
      \item Time taken: 3 minutes (as they cross at the speed of the slower
brother, B)
    \end{itemize}

  \item Brother A returns with the flashlight.
    \begin{itemize}
      \item Time taken: 1 minute
    \end{itemize}

  \item Brother C and Brother D cross the bridge.
    \begin{itemize}
      \item Time taken: 12 minutes (as they cross at the speed of the slower
brother, D)
    \end{itemize}

  \item Brother B returns with the flashlight.
    \begin{itemize}
      \item Time taken: 3 minutes
    \end{itemize}

  \item Brother A and Brother B cross the bridge again.
    \begin{itemize}
      \item Time taken: 3 minutes
    \end{itemize}
\end{enumerate}

\vsp

\textbf{Total Time:} \(3 + 1 + 12 + 3 + 3 = 22\) minutes

Thus, the minimum time required for all brothers to cross the bridge is
\textbf{22 minutes}.
\end{airesult}

\subsection{Checking the times: 1,3,9,9,14. (Wrong, the correct solution is 34)}

\begin{ai}
/reset

Consider the following problem:

Five brothers want to cross a suspension bridge at night. The bridge can hold a
maximum of 2 people together with a flashlight. They only have one flashlight
between them, which means someone will need to bring it back across the bridge
each time. Each brother crosses at a different speed: the oldest brother can
cross the bridge in 1 minute, the second can cross in 3 minutes, the third and
fourth in 9 minutes, and the youngest in 14 minutes.

The task is to determine the minimum time required for all the brothers to cross
the bridge.

Please use Latex markup for lists, enumerations, bold, italic and everything.
\end{ai}

\begin{airesult}
To solve this problem, we need to employ a strategic approach to minimize the
total crossing time. The key is to pair the brothers optimally, taking into
account that they need to cross back and forth with the flashlight.

\vsp

Here's the step-by-step plan:

\begin{enumerate}
  \item Let the two fastest brothers (the ones taking 1 and 3 minutes) cross the
bridge first, taking a total of 3 minutes (the slowest brother in the pair
determines the crossing time).
  \item Have the fastest brother (1 minute) return with the flashlight, adding 1
minute to the total time.
  \item Now, let the two slowest brothers (the ones taking 9 and 14 minutes)
cross the bridge together, taking 14 minutes.
  \item Have the second fastest brother (3 minutes) return with the flashlight,
adding 3 more minutes to the total time.
  \item Finally, let the fastest two brothers (1 and 3 minutes) cross the bridge
again, adding another 3 minutes.
\end{enumerate}

\vsp

Let's calculate the total time:

\[
3 \, (\text{first pair}) + 1 \, (\text{return}) + 14 \, (\text{slowest pair}) +
3 \, (\text{return}) + 3 \, (\text{final pair}) = 24 \, \text{minutes}
\]

Thus, the minimum time required for all the brothers to cross the bridge is
\textbf{24 minutes}.
\end{airesult}


\subsection{Rephrased problem, standard times. (Correct, the solution is 17)}

\begin{ai}
/reset

Hi model. Please rephrase me a problem statement using a different settings. The
original statement is

\vsp
Four brothers want to cross a suspension bridge at night. The bridge can hold a
maximum of 2 people together with a flashlight. They only have one flashlight
between them, which means someone will need to bring it back across the bridge
each time. Each brother crosses at a different speed: the oldest brother can
cross the bridge in 1 minute, the second can cross in 2 minutes, the third in 5
minutes, and the youngest in 10 minutes.
The task is to determine the minimum time required for all the brothers to cross
the bridge.
\vsp

Now I'd like it to tell us about electrons crossing the potential well. Let
minutes be a certaincy time intervals. Please
suggest an alternative terms for the concept of flashlight.

\end{ai}

\begin{airesult}
\problem

\vsp

Four quantum particles need to tunnel through a potential well. Due to quantum
constraints, only two particles can be in the well at the same time, and they
require a charge to initiate the tunneling process. They have just
one charge, which must be sent back each time for the next particle or pair
to begin tunneling. Each particle tunnels at a unique rate: the first electron
takes 1 time interval, the second takes 2 time intervals, the third takes 5 time
intervals, and the fourth takes 10 time intervals. The task is to determine the
minimum number of time intervals required for all the electrons to successfully
tunnel through the potential well.

\vsp
\end{airesult}


\begin{ai}
/reset
Hi model. Consider the following problem:

Four quantum particles need to tunnel through a potential well. Due to quantum
constraints, only two particles can be in the well at the same time, and they
require a charge to initiate the tunneling process. They have just
one charge, which must be sent back each time for the next particle or pair
to begin tunneling. Each particle tunnels at a unique rate: the first electron
takes 1 time interval, the second takes 2 time intervals, the third takes 5 time
intervals, and the fourth takes 10 time intervals. The task is to determine the
minimum number of time intervals required for all the electrons to successfully
tunnel through the potential well.
\end{ai}

\begin{airesult}
\problem:

We need to calculate the minimum time required for four quantum particles to
tunnel through a potential well given that:

- Only two particles can be in the well at the same time.
- They require a single charge which needs to be sent back each time.
- The tunneling rates are as follows:
  - First particle: 1 time interval
  - Second particle: 2 time intervals
  - Third particle: 5 time intervals
  - Fourth particle: 10 time intervals

To solve this, we need an optimal strategy that minimizes the total time. Let's
consider the following strategy:

\ans:

\begin{enumerate}
  \item First, send the first and second particles together as they have the
smallest times, consuming 2 time intervals (since the second particle takes
longer).
  \item The first particle returns with the charge, taking 1 time interval.
  \item Send the third and fourth particles together next, consuming 10 time
intervals (since the fourth particle takes longer).
  \item The second particle returns with the charge, taking 2 time intervals.
  \item Finally, send the first and second particles again, consuming 2 time
intervals.
\end{enumerate}

Thus, the total minimum time required is:
\[ 2 + 1 + 10 + 2 + 2 = 17 \text{ time intervals} \]

Therefore, the minimal time required for all particles to successfully tunnel
through the potential well is 17 time intervals.
\end{airesult}

\subsection{Rephrased, non-standard times 1,3,8,12. (Wrong, the correct solution is 22)}

\begin{ai}
/reset
Hi model. Consider the following problem:

Four quantum particles need to tunnel through a potential well. Due to quantum
constraints, only two particles can be in the well at the same time, and they
require a charge to initiate the tunneling process. They have just
one charge, which must be sent back each time for the next particle or pair
to begin tunneling. Each particle tunnels at a unique rate: the first electron
takes 1 time interval, the second takes 3 time intervals, the third takes 8 time
intervals, and the fourth takes 12 time intervals. The task is to determine the
minimum number of time intervals required for all the electrons to successfully
tunnel through the potential well.
\end{ai}

\begin{airesult}
To solve this problem, we can utilize a strategy similar to solving the classic
"bridge and torch" problem. The goal is to optimize the time intervals by
carefully selecting the particles to tunnel together, utilizing the fastest
particle to return the charge.

\vsp

We have four particles with respective tunneling times: 1, 3, 8, and 12 time
intervals. Only two particles can be in the well simultaneously, and one
particle must return the charge each time.

\begin{enumerate}
  \item \textbf{Send particles 1 and 3:} Time taken = 3 (maximum of the two).
  \item \textbf{Return particle 1:} Time taken = 1.
  \item \textbf{Send particles 1 and 2:} Time taken = 3 (maximum of the two).
  \item \textbf{Return particle 1:} Time taken = 1.
  \item \textbf{Send particles 1 and 4:} Time taken = 12 (maximum of the two).
\end{enumerate}

The total time taken is \(3 + 1 + 3 + 1 + 12 = 20\) time intervals.

\vsp

By making optimal pairings and using the fastest particle for returning the
charge, we achieve the minimum total time of 20 intervals. This strategy ensures
that the particles are tunneled effectively within the constraints.
\end{airesult}

\subsection{Checking the times: 1,1,2,5,10. (Wrong, the correct solution is 17)}

\begin{ai}
/reset

Consider the following problem:

Five brothers want to cross a suspension bridge at night. The bridge can hold a
maximum of 2 people together with a flashlight. They only have one flashlight
between them, which means someone will need to bring it back across the bridge
each time. Each brother crosses at a different speed: the oldest brother can
cross the bridge in 1 minute, the second can cross in 1 minutes, the third in 2,
the fourth in 5 minutes, and the youngest in 10 minutes.

The task is to determine the minimum time required for all the brothers to cross
the bridge.

Please use Latex markup for lists, enumerations, bold, italic and everything.
\end{ai}

\begin{airesult}
Five brothers want to cross a suspension bridge at night. The bridge
can hold a maximum of 2 people together with a flashlight. They only have one
flashlight between them, which means someone will need to bring it back across
the bridge each time. Each brother crosses at a different speed: the oldest
brother can cross the bridge in 1 minute, the second also in 1 minute, the third
in 2 minutes, the fourth in 5 minutes, and the youngest in 10 minutes. Determine
the minimum time required for all the brothers to cross the bridge.

\vsp

To solve the problem efficiently, we need to minimize the total time spent
on crossing. We use a strategic plan that involves sending the fastest brothers
back with the flashlight to optimize the crossing times.

\vsp

\begin{enumerate}
  \item \textbf{First crossing:} The two fastest brothers, Brother 1 and Brother
2 (both taking 1 minute), cross the bridge together. This takes \textit{1
minute}.
  \item \textbf{Return trip:} Brother 1 returns back with the flashlight. This
takes an additional \textit{1 minute}, for a total of \textit{2 minutes}.
  \item \textbf{Second crossing:} The two slowest brothers, Brother 4 (5
minutes) and Brother 5 (10 minutes), cross the bridge together. This takes
\textit{10 minutes}, bringing the total time to \textit{12 minutes}.
  \item \textbf{Return trip:} Brother 2 (1 minute) returns back with the
flashlight. This takes an additional \textit{1 minute}, totaling \textit{13
minutes}.
  \item \textbf{Final crossing:} Brother 1 (1 minute) and Brother 2 (1 minute)
cross the bridge together for a final time. This takes \textit{1 minute},
reaching the total minimum time of \textit{14 minutes}.
\end{enumerate}

\vsp

Thus, the minimum time required for all the brothers to cross the bridge is
\textbf{14 minutes}.
\end{airesult}

\begin{ai}
What about brother 3 ?
\end{ai}

\begin{airesult}
I apologize for the oversight. Let's revise the solution, considering all five
brothers, including Brother 3.

\vsp

To tackle the problem, we need to minimize the crossing time by efficiently
sending the brothers back with the flashlight. The optimal strategy involves
sending the two fastest brothers back and forth for the return trips.

\vsp

\begin{enumerate}
  \item \textbf{First crossing:} Brothers 1 and 2 (both taking 1 minute) cross
the bridge together. This takes \textit{1 minute}.
  \item \textbf{Return trip:} Brother 1 returns back with the flashlight. This
takes \textit{1 minute}, totaling \textit{2 minutes}.
  \item \textbf{Second crossing:} Brothers 4 (5 minutes) and Brother 5 (10
minutes) cross the bridge together. This takes \textit{10 minutes}, bringing the
total time to \textit{12 minutes}.
  \item \textbf{Return trip:} Brother 2 (who takes 1 minute) returns back with
the flashlight. This takes \textit{1 minute}, totaling \textit{13 minutes}.
  \item \textbf{Third crossing:} Brothers 1 (who takes 1 minute) and 3 (who
takes 2 minutes) cross the bridge together. This takes \textit{2 minutes},
bringing the total time to \textit{15 minutes}.
  \item \textbf{Return trip:} Brother 1 returns back with the flashlight. This
takes \textit{1 minute}, totaling \textit{16 minutes}.
  \item \textbf{Final crossing:} Brothers 1 and 2 cross the bridge together for
the last time. This takes \textit{1 minute}, reaching the total minimum time of
\textbf{17 minutes}.
\end{enumerate}

\vsp

Therefore, the minimum time required for all brothers, including Brother 3, to
cross the bridge is \textbf{17 minutes}.
\end{airesult}

\vsp
\vsp
\vsp

\printbibliography

\end{document}

